\documentclass[10pt,twocolumn]{article} 

% use the oxycomps style file
\usepackage{oxycomps}

% read references.bib for the bibtex data
\bibliography{references}

% include metadata in the generated pdf file
\pdfinfo{
    /Title (Literary Review for Nirvana Machinas)
    /Author (Victor Zhu)
}

% set the title and author information
\title{Literary Review for Nirvana Machinas}
\author{Victor Zhu}
\affiliation{Occidental College}
\email{hzhu@oxy.edu}

\begin{document}

\maketitle


\section{Introduction}

Nirvana Machinas is a game that consist of elements of Rouglite, card deck collection, and bullet hell. The in-game goal is to travel across the post-apocalyptic wasteland to upload the player’s consciousness to an extraterrestrial server in order to achieve "Nirvana into the machines"(Nirvana Machinas). In the game, the players are on their journey of pilgrimage, it mirrors the pilgrimage we called life. The player is given a set of cards at the beginning and gain more from combat or special events in game. The player will be using these cards to fight most of his obstacles such as bandits, heretics and/or monsters of radiation, etc. The player is a monk, pilgrim, zealot, ascetic who seeks peace and ascension in the post-apocalyptic wasteland. The monk must travel through three different areas, the Wastes, full of bandits and feral animals, the Nuclear Hell, where consist of heretics and mosters mutated past recognition. The final level is the Sea of Misery. the bomb crater that carries radiatioactive water ,ill-wired robots and more heretics. After the three levels, the player will reach the data center and upload his consinouss.
\section{Problem contexts}
Nirvana Machinas is consist of complex arrays of video game mechniacs. Niravana Machinas is first a rogue-lite game. Rogue-lite is a subgenre of Roguelike game. Roguelike is a subgenre of role-playing video games characterized by permanent death of the player character.(1) The name ""Rogue-like" comes from the game Rogue(1980) which features dungeon crawl through procedurally generated levels, turn-based gameplay, grid-based movement and permant death. Other famous one of the Rogue-like genre includes Nethacks, Mystery Dungeon etc. Rogue-lite is a subgenre of Roguelike which signature is player is able to acess the progession elements after the player's death. After each playthrough in Nirvana Machinas, player will be rewarded with points that can unlock more artifacts and cards. The main mechniacs of Nirvana Machinas is card deck collection. The card-deck collection genre has a long history. In a way, poker is also card-deck collection game. This genre is define card-based game play and collection of cards as the player progess. In Nirvana Machinas, the player has to use card to combat their enenmy and get new cards after wining or special event. Nirvana Machinas also consists of bullethell elements. Bullet Hell refers to a sub-genre of shooters whose main gameplay focus is dodging seemingly endless waves of bullets.(2) One of example game of this genre is Touhou Project. In the game, the player has to go through special bullethell levels in order to get new sets of cards.





\section{Techolocial background}

This game will be using Unity as the engine for its adaptability and availability. I will use C+ scripts to code movement for characters. The character art is drawn by my partner Mattew Perez. The monk and first encounter enemies are drawn in sprite render in unity hub. All their movement is done in c+ scripts as the character’s movement is rather minimal. The card and its logic are also done in the C+ scripts.


\section{Prior Work  }
*Slay the Spire*
Slay the Spire creates new genre by combine roguelite and card-deck collection game. Its undoubtly success inspires many slimaliar games like: Griftland ,the Night of Fullmoon , Blackbook etc. The game consists 4 characters: Ironclad,Silent,Defect, Watcher. Each of them has its unqiue mechanic, cards and artifacts. This game creates a new combats system that are much fited for single player. The enemy instead of using another set of playing card, they have predetemined actions. Their predetemed action can be serpated in 3 category: attack, defence and special effect. The enemies will also display their intension on the top of their head. With this inovative gameplay, the developer will spend less time designing enemie 's combat tatic and therefore easily regulate the balance of cards.
*The binding of Issac*
	The binding of Isaac is also one of the most influential independent games of the current generation. The game is a combination of rogue-like and bullet hell with religouious element. The story is about a child escaping from being sacrifice by his parent, parallel to the legend of issac in the bible. In the game the child has to fight through the “basement”  The basement is divided into a series of single chambers, with a world design that is reminiscent to the Legend of Zelda's dungeons. In actuality, the game is divided into several levels, each with an end boss to defeat before continuing. Long-time gamers will feel right at home with Isaac's traditions, which include bombs, treasure boxes, and even keys.
 

\end{document}
